### 2020-01-31 report/02-methods.Rmd
Try to cover some issues with sampling effort

>>>>

## Fishing methods

```{r}
myload(env_analysis, biomass_ts_sax, dir = data_common)
```

```{r}
census <- op_analysis %>%
  left_join(select(env_analysis, station, opcod, width_river))

census %>%
  ggplot(aes(y = length_sourced, x = width_river, color = protocol_type)) +
  scale_x_log10() +
  scale_y_log10() +
  geom_point()
```

```{r}
census %>%
  group_by(station) %>%
  arrange(year) %>%
  nest()
bm_census <-  biomass_ts_sax %>%
  unnest(data) %>%
  left_join(mutate(census, station = as.character(station)),
    by = c("station", "date"))
```

```{r}
# Test how sampled effort is linked to biomass
mod_bm_census <- bm_census %>%
  group_by(station, protocol_type) %>%
  #mutate(biomass = scale(biomass)) %>%
  nest() %>%
  filter(!is.na(station)) %>%
  mutate(
    mod_w_l = map(data, ~lm(length_sourced ~ width_river, data = .x)),
    data_w_l = map(mod_w_l, broom::augment),
    data_resid = map2(data, data_w_l,
      function(raw, augmented) {
	raw$resid_length <- augmented[[".resid"]]
        return(raw)
      }),
    model = map(data_resid, ~lm(biomass ~ resid_length, data = .x)),
    coeff = map(model, broom::tidy),
    summary = map(model, broom::glance)
  )

mod_bm_census %>%
  unnest(coeff) %>%
  #rename(interp = `(Intercept)`, slope = length_sourced) %>%
  filter(! term %in% "(Intercept)") %>%
  mutate(effect_size = estimate / std.error) %>%
  #select(station, term, estimate) %>%
  #spread(term, estimate) %>%
  ggplot(aes(x = estimate)) +
  geom_histogram() +
  geom_vline(aes(xintercept = mean(estimate)))

```{r}

mod_bm_census %>%
  unnest(coeff) %>%
  filter(! term %in% "(Intercept)")

residuals(mod_bm_census$model[[9]])
mod_bm_census$model[[9]]
mod_bm_census$data[[9]]
```

### 2020-01-31 report/03-results.Rmd
Try to cover some issues with sampling effort

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, dir = data_common)
```

@@

```{r more-stab-troph, fig.dim = c(10, 21), fig.cap = "The four station with the highest biomass stability. Dashed and solid lines represent respectively trophic species in the group 2 and 3."}

# Get biomass by sp node:
net_sp_troph <- select(network_analysis, opcod, composition) %>%
  unnest(composition)
# Get synchrony and cv sp:
sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis)
# Get trophic lvl by node
trophic_level %<>%
  rename(species = sp_class) %>%
  mutate(troph_group = get_size_class(trophic_level, NULL, troph_level,
      trophic_class))

>>>>

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, dir = data_common)
source(mypath("R", "local_network_build.R"))
```

@@

```{r more-stab-troph, fig.dim = c(10, 21), fig.cap = "The four station with the highest biomass stability. Dashed and solid lines represent respectively trophic species in the group 2 and 3."}
myload(trophic_level, trophic_class, dir = mypath("data"))
# Get biomass by sp node:
net_sp_troph <- select(network_analysis, opcod, composition) %>%
  unnest(composition)
# Get synchrony and cv sp:
sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis)
# Get trophic lvl by node
trophic_level %<>%
  rename(species = sp_class) %>%
  mutate(troph_group = get_size_class(trophic_level, NULL, troph_level,
      trophic_class))

### 2020-01-31 report/05-stability.Rmd
Try to cover some issues with sampling effort

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload( trophic_level, trophic_class, dir = mypath("data"))
myload(hab_type, habitat_pressure, dir = mypath("report"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "local_network_build.R"))
stab_div_troph <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) 
```

@@

@@

The relationship between stability and species diversity (Figure
\@ref(fig:bimod-stab-div)) seemed to work only in station far from the source
(which are deeper, hotter, wider, fig. \@ref(fig:pca-hab))). It should be the
place where the ANG is the most present. The ANG were effectively more abundant
in the latter station (Figure: \@ref(fig:ang-map-bio)).

@@

@@

@@

```{r abun-sp, fig.dim = c(10, 7), fig.cap = "Species most abundant by trophic group."}
# Sp the most abundant by group
bm_sp_troph_grp <- net_sp_troph %>%
  filter(!is.na(troph_group) & troph_group != 1) %>%
  group_by(troph_group, sp_class, opcod) %>%
  mutate(rel_biomass = biomass / sum(biomass)) %>%
  group_by(troph_group, sp_class) %>%
  summarise(sum_rel_bm = sum(rel_biomass), biomass = mean(biomass)) %>%
  arrange(desc(sum_rel_bm)) %>%
  slice(1:20)

@@

st_basin <- get_basin_station()
myload(nmds, dir = mypath("report"))

# Compute stability, network metrics, etc with the new datasets
com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "species"))

# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]], 
  hab_press = habitat_pressure, 
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin 
  )

>>>>

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, temporal_community_metrics, synchrony, op_analysis, dir = data_common)
myload(network_analysis, dir = mypath("data", "classes"))
myload(trophic_level, trophic_class, dir = mypath("data"))
myload(hab_type, habitat_pressure, dir = mypath("report"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "local_network_build.R"))
stab_div_troph <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group)) 
```

@@

### Stability by habitat type

@@

The relationship between stability and species diversity (Figure
\@ref(fig:bimod-stab-div)) seemed to work only in station far from the source
(which are deeper, hotter, wider, fig. \@ref(fig:pca-hab))). May be there are
difference in richness distribution.

```{r}
plot_bin_rich_div <- function (env = NULL) {

  habitat_pressure$env_bin <- ifelse(
    habitat_pressure[[env]] < median(habitat_pressure[[env]], na.rm = TRUE),
    "inf", "sup")
  habitat_pressure <- na.omit(habitat_pressure[, c("station", "env_bin")])
  habitat_pressure %>%
    left_join(stab_div_basin, by = "station") %>%
    ggplot(aes(x = richness_avg, color = troph_group)) +
    geom_histogram() +
    facet_grid(cols = vars(env_bin)) +
    ggplot2::scale_color_manual(
      labels = troph_group_labeller(),
      values = c("blue", "green", "red"),
      name = "Trophic level"
    ) +
  labs(title = env, x = "Average species richness", y = "Frequency") +
  theme(legend.position = "none")
}

mult_plot_rich_div_bin <- map(env, ~plot_bin_rich_div(env = .x))
plot_grid(plotlist = mult_plot_rich_div_bin, ncol = 2)
```

@@

```{r, fig.cap = "histogram of species occurence by station"}
hist(as.matrix(occurence_sp_st[, !names(occurence_sp_st) %in% "station"])) 
```

```{r, fig.dim = c(14, 14), fig.cap = "Histogram of species evaluation"}
occurence_sp_st[, !names(occurence_sp_st) %in% "station"] %>%
  gather(species, occurence) %>%
  ggplot(aes(x = occurence)) +
  geom_histogram() +
  geom_vline(data = rename(global_med_occ, species = sp, occurence = med_occ),
    aes(xintercept = occurence), color = "red") +
  facet_wrap(~species, scales = "free_y")
```

@@

#### Remove most abundant species

```{r}
threshold_occ <- c(.50, .80, .90, 1)
com_wo_core  <- map(threshold_occ, 
  ~rm_sp_from_com(com = ungroup(community_analysis), sp_to_rm =
    global_med_occ[global_med_occ$med_occ > .x,]$sp))
names(com_wo_core) <- threshold_occ

res_sync_core <- map2_dfr(com_wo_core, names(com_wo_core), function (.data, .names) {

  sync <- compute_com_synchrony(
    .op = op_analysis,
    com = .data, presence_threshold = NA)
  sync$type <- .names 
  sync$biomass_stab <- 1 / sync$cv_com
  return(sync)

p_sync_global_core <- res_sync_core %>%
  ggplot(aes(x = richness_med, y = biomass_stab)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  facet_grid(cols = vars(type))

p_sync_global_core

#### Remove low richness

```{r}
sync_rm <- map_dfr(seq(0, 10, 1),
  function (x)
    filter(synchrony, !richness_tot < x) %>%
      mutate(min_rich = x) 
)
sync_rm_res <- sync_rm %>%
  mutate(
    log_rich = log10(richness_med),
    log_stab = log10(1/cv_com)) %>%
  group_by(min_rich) %>%
  nest() %>%
  mutate(
    model = map(data, ~ lm(log_stab ~ log_rich, .x)),
    coeff = map(model, broom::tidy),
    plot = map2(.x = data, .y = min_rich,
      ~ .x %>%
	ggplot(aes(x = richness_med, y = 1/cv_com)) +
	geom_point() +
	geom_smooth(method = "lm") +
	stat_poly_eq(
	  formula = y ~ x,
	  eq.with.lhs = "italic(hat(y))~`=`~",
	  aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
	  parse = TRUE) +
	labs(title = .y)
      )
  )
plot_grid(plotlist = sync_rm_res$plot)
```

```{r}
sync_rm_res %>%
  unnest(coeff) %>%
  rename(est = estimate, se = std.error) %>%
  filter(term == "log_rich") %>%
  ggplot(aes(y = est, x = min_rich)) +
  geom_point() +
  geom_errorbar(aes(ymin = est - 2 * se, ymax = est + 2 * se)) +
  geom_hline(yintercept = 0) +
  labs(y = "Slope of linear relationship between Biomass stability and median species richness ()")
```

In fact, the removal of low species station has an notable effect if the
richness cut was done on median richness. However, if total richness is
considered, the removal has far less effect.

@@

```{r abun-sp, fig.dim = c(10, 7), fig.cap = "Species most abundant by trophic group."}
net_sp_troph <- select(network_analysis, opcod, composition) %>%
  unnest(composition)
# Get synchrony and cv sp:
sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis)
# Sp the most abundant by group
bm_sp_troph_grp <- net_sp_troph %>%
  filter(!is.na(troph_group) & troph_group != 1) %>%
  group_by(troph_group, sp_class, opcod) %>%
  mutate(rel_biomass = biomass / sum(biomass)) %>%
  group_by(troph_group, sp_class) %>%
  summarise(sum_rel_bm = sum(rel_biomass), biomass = mean(biomass)) %>%
  arrange(desc(sum_rel_bm)) %>%
  slice(1:20)

@@

st_basin <- get_basin_station()
myload(nmds, dir = mypath("report"))
myload(network_metrics, dir = mypath("data", "species"))

# Compute stability, network metrics, etc with the new datasets
com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "species"))
# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]], 
  hab_press = habitat_pressure, 
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin 
  )
